---
title: "Movies and Ratings"
output:
  html_document: default
  pdf_document: default
---
## Setup 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(tidyverse)
library(here)
library(reprex)
```

```{r data_read}
Movie <- read.csv(here("Data","Movie Ratings.csv"))
head(Movie)
IMDB <- read.csv(here("Data", "imdb_1000.csv"))
```

## The Data
Movie_Ratings.csv

Download link:  https://www.dropbox.com/s/ebr2gzy95pb9lsx/Movie%20Ratings.csv?dl=1 

Variables:

* Film - The title of a film.
* Genre - The film's primary genre.
* Rotten Tomatoes % - The average movie rating from critics on Rotten Tomatoes, from 0-100.
* Audience Ratings % - The average movie rating voted by audience members on Rotten Tomatoes, from 0-100.
* Budget (million $) - The operating budget of the movie.
* Year of release - The year the movie hit theaters.
 

imdb_1000.csv

Download link: https://www.dropbox.com/s/ov5cntaof9lj9v6/imdb_1000.csv?dl=1 

Variables:

* star_rating - The rating of the movie from user votes on imdb.com.  (0-10)
* title - The title of the film
* content_rating - The designation of the movie from the Motion Picture Association.
* genre - The primary genre of the film.
* duration - The length of the film, in minutes
* actors_list - The leading actors credited in the movie.

## The Tasks

#### Cleaning/Plotting

1.  Read in and summarize the data.

```{r cleaning/plotting1}
Movie %>%
  summary()
IMDB %>%
  summary()
```

2.  What genre had the highest average imdb rating?

```{r cleaning/plotting2}
IMDB %>%
  group_by(genre) %>%
  summarise(mean=mean(star_rating)) %>%
  arrange(desc(mean))

```
Ans. Western

3.  Is there a relationship between the content rating of the movie (e.g. "PG-13") and its duration?  Make a plot.

```{r cleaning/plotting3}
IMDB %>%
  ggplot(aes(x=content_rating, y=duration))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Ans. No relationship

#### Pivoting

1. Make a column plot comparing Rotten Tomato critic and audience ratings for all the Romance movies.

```{r pivoting1}
Movie1 <- Movie %>%
  select(Genre, Film,Rotten.Tomatoes.Ratings..,Audience.Ratings..) %>%
  filter(Genre=="Romance") %>%
  pivot_longer(Rotten.Tomatoes.Ratings..:Audience.Ratings.., names_to = 'Ratings', values_to = 'Rating_value')
  
Movie1 %>%
  ggplot(aes(x = `Rating_value`,y = Film, fill = Ratings )) +
  geom_col()
```

2. For each year, find the average audience rating difference between Comedy and Drama movies.

```{r pivoting2}
Movie %>%
  filter(Genre == c('Comedy','Drama')) %>%
  group_by(`Year.of.release`, Genre) %>%
  summarise(Mean_Aud_Rating = mean(Audience.Ratings.. )) %>%
  pivot_wider(names_from = Genre, values_from = Mean_Aud_Rating) %>%
  mutate(`Mean_Aud_Rating_Diff` = Drama - Comedy)
```

#### Joining

1. How many movies appear in both datasets?

```{r joining1}
Movie_1 <- Movie %>%
  select(Film)
IMDB_1 <- IMDB %>%
  select(title)

MovieT <- inner_join(Movie_1,IMDB_1,by = c("Film"="title"))

length(unique(MovieT$Film))
```

2. How many movies appear in only the imdb dataset?

```{r joining2}
length(unique(IMDB_1$title))
```

3. How many movies appear in only the Rotten Tomatoes dataset?

```{r joining3}
length(unique(Movie_1$Film))
```

## Joining and pivoting

Make a plot comparing the ratings from Rotten Tomatoes Critics, Rotten Tomatoes Audience, and imdb.

```{r joining&pivoting}
Compare1 <-
  inner_join(Movie, IMDB, by = c('Film' = 'title'))

Compare2 <- Compare1 %>% 
  mutate(star_rating = star_rating*10) %>%
  select(Genre,Rotten.Tomatoes.Ratings.., Audience.Ratings..,star_rating)
  
Compare3 <- Compare2 %>%
  pivot_longer(Rotten.Tomatoes.Ratings..: star_rating, names_to = 'Rating_Name', values_to = 'Rating_Value') %>%
  group_by(Genre, Rating_Name) %>%
  summarise(mean_Rating_Value = as.integer(mean(Rating_Value)))

Compare3

Compare3 %>% 
  ggplot() +
  geom_col(aes(x= Genre, y = mean_Rating_Value, fill = Rating_Name), position = 'dodge')

```
